### 2022-12-04 ms.rmd
Added new models for assessing autocorrelations in climate and Q10

  } else{
        model3.4 <- readRDS("./output/models/lnRRQ10_3.4")
  model3.4_bayes <- readRDS("./output/models/lnRRQ10_3.4_bayes")
}
```

>>>>

  } else{
        model3.4 <- readRDS("./output/models/lnRRQ10_3.4")
  model3.4_bayes <- readRDS("./output/models/lnRRQ10_3.4_bayes")
  }

if(rerun){
  # More realistic model with 
  model3.5          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(cv) + type, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild)

   model3.5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(cv) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)

  # Save model3.5
  saveRDS(model3.5, file = "./output/models/lnRRQ10_3.5")
  saveRDS(model3.5_bayes, file = "./output/models/lnRRQ10_3.5_bayes")

  } else{
        model3.5 <- readRDS("./output/models/lnRRQ10_3.5")
  model3.5_bayes <- readRDS("./output/models/lnRRQ10_3.5_bayes")
  }

  if(rerun){
  # More realistic model with 
  model3.6          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + type, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild)

   model3.6_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)

  # Save model3.6
  saveRDS(model3.6, file = "./output/models/lnRRQ10_3.6")
  saveRDS(model3.6_bayes, file = "./output/models/lnRRQ10_3.6_bayes")

  } else{
        model3.6 <- readRDS("./output/models/lnRRQ10_3.6")
  model3.6_bayes <- readRDS("./output/models/lnRRQ10_3.6_bayes")
}
```
